---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# os.pca

<!-- badges: start -->
<!-- badges: end -->

`os.pca` is a wrapper package for `homals`, and modifies and scales the output to align with optimal scaling PCA. Includes plot functions and extra outputs.

## Installation

You can install the development version of os.pca from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("laurazwep/os.pca")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(os.pca)
```

Create example data

```{r}
set.seed(123)
n <- 500
x1_cat <- sample(c(1, 2, 3), size = n, replace = TRUE)
x2 <- x1_cat*4 + rnorm(n)
x1_cat <- factor(x1_cat, labels = c("B", "A", "C"))
x1_cat <- relevel(x1_cat, ref = "A")
test_data <- data.frame(x1 = x1_cat, x2 = x2)

plot(test_data)
```

Apply os.copula

```{r}
output_nom <- os_pca(data = test_data, level = c("nominal", "numerical"), ndim = 1)
```
Plot functions

```{r}
plot.os_catquants(output_nom, plot_vars = 1, rcplot = c(1, 1))
```
```{r}
plot.os_loadings(output_nom)
```



